---
title: "Regression"
output: html_document
runtime: shiny
---

# Introduction to regression

We're going to follow along the analysis [here](https://www.opencasestudies.org/ocs-bp-RTC-analysis/) as we build towards multivariable regression. This data studies 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warnings = FALSE)
```

```{r}
library(tidyverse)
library(shiny)
```

```{r}
load(url("https://github.com/opencasestudies/ocs-bp-RTC-analysis/blob/master/data/Wrangled_data.rda?raw=true"))
```

Let's create a basic data set looking at the natural log of 
violent crime trends over time.
```{r}
regDat = DONOHUE_DF %>%
  group_by(YEAR) %>%
  summarize(Viol_crime_count = sum(Viol_crime_count),
                  Population = sum(Population),
                    .groups = "drop") %>%
  mutate(Viol_crime_rate_100k_log = log((Viol_crime_count*100000)/Population))

g = regDat %>% ggplot(aes(x = YEAR, y = Viol_crime_rate_100k_log)) +
  geom_line() +
  scale_x_continuous(breaks = seq(1980, 2010, by = 1),
                     limits = c(1980, 2010),
                     labels = c(seq(1980, 2010, by = 1))) +
  scale_y_continuous(breaks = seq(5.75, 6.75, by = 0.25),
                     limits = c(5.75, 6.75)) +
  labs(title = "Crime rates fluctuate over time",
       x = "Year",
       y = "ln(violent crimes per 100,000 people)") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90))
g
```

For the purposes of this lecture, let's rename the log violent crime rate as Y and the
year as X. 

```{r}
regDat = regDat %>% select(x = YEAR, y = Viol_crime_rate_100k_log)
head(regDat)
```

Consider ignoring year altogether and only worrying about the violent crime rate.
We want to minimize $\sum_i (y_i - \mu)^2$ over $\mu$.

```{r echo=FALSE}
y = regDat$y
ymin = round(min(y), 2)
ymax = round(max(y), 2)
ymean = mean(y)
inputPanel(
  sliderInput("mu", label = "Mu:",
              min = ymin, max = ymax, value = ymean, step = 0.01)
)


renderPlot({
  mse = mean( (y - input$mu) ^ 2 )
  plt = density(y)
  plot(range(plt$x), range(plt$y), type = "n", frame = FALSE)
  xlab("y")
  lines(plt, lwd = 2)
  title(paste("MSE: ", round(mse, 3)))
  abline(v = ymean, col = "blue", lwd = 2)
  abline(v = input$mu, col = "red", lwd = 2)
})
```

No need to optimize this directly, since we know the answer.
$$
\begin{align}
\sum_{i=1}^n (y_i - \mu)^2 & =  \sum_i (y_i - \bar y + \bar y - \mu)^2 \\
                     & = \sum_i (y_i - \bar y)^ 2 + 2(\bar y - \mu) \sum_i (y_i - \bar y)
                        + n (\bar y - \mu)^2 \\
                     & = \sum_i (y_i - \bar y)^ 2 + n (\bar y - \mu)^2 \\
                     & \leq \sum_i (y_i - \bar y)^ 2.
\end{align}
$$
Now let's consider a regression variation of the problem. Assume we want to minimize
$\sum_i (y_i - \beta_0 - \beta_1 x_i)^2$. That is, we want to find the best line
that fits our data.

```{r echo=FALSE}
y = regDat$y
x = regDat$x
x = x - mean(x)


inputPanel(
  sliderInput("b0", label = "Beta0",
              min = 6.2, max = 6.8, value = 6.36430, step = .01),
  sliderInput("b1", label = "Beta1",
              max = 0, min = -.03, value = -0.01249, step = 0.005)
)

renderText(c(input$b0 - 31.28037))
renderPlot({
  mse = mean( (y - input$b0 - input$b1) ^ 2 )
  plot(x, y, frame = FALSE, ylim = c(6, 8), xlab = "years since 1980")
  title(paste("MSE: ", round(mse, 3)))
  abline(6.36430, -0.01249, col = "blue", lwd = 2)
  abline(input$b0, input$b1, col = "red", lwd = 2)
})
```
