---
title: "python 4 R users"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}
library(tidyverse)
library(reticulate)
use_python("/usr/bin/python3")
## Not set b/c I don't have a specific conda environment
#use_virtualenv("myenv")
```

```{r}
if (!file.exists("kirbyExample.csv"))
  download.file("https://raw.githubusercontent.com/bcaffo/ds4bme_intro/master/data/kirby127a_3_1_ax_283Labels_M2_corrected_stats.csv", destfile = "kirbyExample.csv")
```

# Using python in R markdown

Use Python to read in the file and do some data manipulation

```{python}
import pandas as pd
df = pd.read_csv("kirbyExample.csv")
df.head(4)
df = df.drop(['Unnamed: 0', 'rawid', 'min', 'max', 'mean', 'std'],axis = 1)
t1l1 = df.loc[(df.type == 1) & (df.level == 1)]
## Create a new column based on ICV
t1l1 = t1l1.assign(icv = sum(t1l1.volume))
t1l1 = t1l1.assign(tbv = sum(t1l1.volume[(t1l1.roi != 'CSF')]))
t1l1 = t1l1.assign(comp = lambda x: x.volume / x.tbv)
t1l1
```

The file is loaded in as an R object now stored in the variable `py`.
```{r}
ggplot(data=py$t1l1, aes(x = roi, y = comp)) + 
  geom_bar(stat="identity")  + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


# Importing python modules


Note for this to work for me, I had to install a newer version of reticulate.
Note that class is read in using pandas, but is a native R data frame.

```{r}
pd = import('pandas')
test = pd$read_csv('kirbyExample.csv')
test
class(test)
```


# Calling python scripts

```{r}
source_python("pythonTestScript.py")
t1l1 = read_subject("kirbyExample.csv")
class(t1l1)
t1l1
```

# Calling the python repl

Not executed, you can call the python repl from the R command. Use `exit` to exit the repl.

```
repl_python()
```

Objects do not have permenancy in R after exiting the python repl.




